### 2016-06-18 paper/icfp16-cameraready/introduction.tex
add NSF acks

\subparagraph{Witness Utility}
%
Even if we can find small witnesses for the majority of type errors, it
may be that the witnesses do not actually help developers
\emph{understand} the errors.
%
In other words, perhaps the static error message is sufficient to
diagnose and fix the error, or perhaps the witness simply does not add
enough information to make a difference.
%
Thus, our final contribution is a user study that compares the utility
of our witnesses with that of the error messages provided by the \ocaml
compiler~(\S~\ref{sec:user-study}).
%
We show that students given one of our witnesses are consistently more
likely to correctly explain and fix a type error than those given
the standard error message produced by the \ocaml compiler.

>>>>

The ultimate purpose of an error report is to assist the programmer 
in \emph{understanding} and \emph{fixing} problematic code.
%
Thus, our final contribution is a user study that compares \ocaml's 
errors and our dynamic witnesses against \ocaml's type errors 
along this dimension~(\S~\ref{sec:user-study}).
%
We show that students given one of our witnesses are consistently more
likely to correctly explain and fix a type error than those given
the standard error message produced by the \ocaml compiler.

% \subparagraph{Witness Utility}
%
Even if we can find small witnesses for the majority of type errors, it
may be that the witnesses do not actually help developers
\emph{understand} the errors.
%
In other words, perhaps the static error message is sufficient to
diagnose and fix the error, or perhaps the witness simply does not add
enough information to make a difference.
%

Thus, our final contribution is a user study that compares the utility
of our witnesses with that of the error messages provided by the \ocaml
compiler~(\S~\ref{sec:user-study}).
%
We show that students given one of our witnesses are consistently more
likely to correctly explain and fix a type error than those given
the standard error message produced by the \ocaml compiler.
